Understanding the Landscape of Childlessness in the U.S.

### 2024-03-18 outputs/paper/paper.qmd
GSS questions added

# Appendix {#sec-appendix}
The supplementary survey is accessible through this link: https://forms.gle/DsFgJCKPeCtdqZKL6

## Survey Preamble
The General Social Survey (GSS) collects data on social trends to help track changes in Canadians' living conditions and well-being over time. Also, it provides information on specific social policy issues that are currently or potentially important.

@@

## Survey Questions for Childlessness

@@

@@

>>>>

# Appendix {#sec-appendix}

## Our Survey for Childlessness Study

The supplementary survey is accessible through this [Google Form Link](https://forms.gle/DsFgJCKPeCtdqZKL6)

### Survey Preamble
The General Social Survey (GSS) collects data on social trends to help track changes in Canadians' living conditions and well-being over time. Also, it provides information on specific social policy issues that are currently or potentially important.

@@

### Survey Questions

@@

### Survey Completion Message

@@

## Survey Questions from GSS

1. RESPONDENT'S AGE: (short answer text)

2. RESPONDENT'S SEX

- Female
- Male

3. Are you currently--married, widowed, divorced, separated, or have you never been married? (short answer text)

4. RESPONDENT'S DEGREE

- Graduate
- Bachelor's
- Associate/junior college
- High school
- Less than high school

5. How many children have you ever had?  Please count all that were born alive at any time (including any you had from a previous marriage).

- 0
- 1
- 2
- 3
- 4
- 5
- 6
- 7
- 8 or more

6. If you were asked to use one of four names for your social class, which would you say you belong in: the lower class, the working class, the middle class, or the upper class? (short answer text)

7. Would you say your own health, in general, is excellent, good, fair, or  poor? (short answer text)
